Exoplanet population inference and the rate of Earth analogs \\ from noisy, incomplete catalogs

### 2014-06-09 document/ms.tex
integrated rates

\newcommand{\dd}{\ensuremath{\,\mathrm{d}}}
\newcommand{\bvec}[1]{\ensuremath{\boldsymbol{#1}}}
\newcommand{\appropto}{\mathrel{\vcenter{
  \offinterlineskip\halign{\hfil$##$\cr
    \propto\cr\noalign{\kern2pt}\sim\cr\noalign{\kern-2pt}}}}}

@@

Our constraint on the rate density of Earth analogs (as defined in
\sect{extrap}) is in tension---even though our result has large fractional
uncertainty---with the result from \citet{petigura}.
This is shown in \fig{real-rate} where we compare the marginalized posterior
probability function for \gammaearth\ to the published value and uncertainty.
Quantitatively, we find that the rate density of Earth analogs is
\begin{eqnarray}
\gammaearth &=& 0.017^{+0.018}_{-0.009} \quad.
\end{eqnarray}
Converted to these units, \citet{petigura} measured $0.119_{-0.046}^{+0.035}$
for the same quantity (indicated as the vertical lines in \fig{real-rate}).

>>>>

\newcommand{\dd}{\ensuremath{\,\mathrm{d}}}
\newcommand{\bvec}[1]{\ensuremath{\boldsymbol{#1}}}
\newcommand{\appropto}{\mathrel{\vcenter{
  \offinterlineskip\halign{\hfil$##$\cr
    \propto\cr\noalign{\kern2pt}\sim\cr\noalign{\kern-2pt}}}}}
\newcommand{\densityunit}{{\ensuremath{\mathrm{nat}^{-2}}}}

@@

Our constraint on the rate density of Earth analogs (as defined in
\sect{extrap}) is in tension---even though our result has large fractional
uncertainty---with the result from \citet{petigura}.
This is shown in \fig{real-rate} where we compare the marginalized posterior
probability function for \gammaearth\ to the published value and uncertainty.
Quantitatively, we find that the rate density of Earth analogs is
\begin{eqnarray}
\gammaearth &=& 0.017^{+0.018}_{-0.009}~\densityunit
\end{eqnarray}
where the ``\densityunit'' indicates that this quantity is a rate density, per
natural logarithmic period per natural logarithmic radius.
Converted to these units, \citet{petigura} measured
$0.119_{-0.046}^{+0.035}~\densityunit$ for the same quantity (indicated as the
vertical lines in \fig{real-rate}).
This rate density is \emph{exactly} what Petigura's extrapolation model
predicts but, for comparison, we can also integrate our inferred rate density
over their choice of ``Earth-like'' bin ($200 \le \period/\mathrm{day} < 400$
and $1 \le \radius/\radius_\oplus < 2$) to find a \emph{rate} of
Earth-analogs.
The published rate is $0.057_{-0.017}^{+0.022}$ (\citealt{petigura}) and our
posterior constraint is
\begin{eqnarray}
\int_{\period=200\,\mathrm{day}}^{400\,\mathrm{day}}
\int_{\radius=1\,\radius_\oplus}^{2\,\radius_\oplus}
\rate_\ratepars (\ln\period,\,\ln\radius)
\dd[\ln\radius]
\dd[\ln\period]
&=&
0.016_{-0.007}^{+0.011}
\quad.
\end{eqnarray}
